### 2012-11-16 doc/progress_plan/report.tex
Finished talking abotu sapienta

SAPIENTA for Python also relies upon a package called CRFSuite which implements
Conditional Random Fields, a method for segmenting and labelling sequence
data\cite{CRFsuite}. This library did not compile properly on the test
environment and its creator had to be contacted via a mailing list (See
Appendix \ref{sec:crfletter}.

>>>>

SAPIENTA for Python also relies upon a package called CRFSuite which implements
Conditional Random Fields, a method for segmenting and labelling sequence
data\cite{CRFsuite}. This library did not compile properly on the test
environment and its creator had to be contacted via a mailing list (See
Appendix \ref{sec:crfletter}. After a few days, the owner responded and the
library was compiled successfully.

Once all the data files and libraries were successfully in place, the Python
version of SAPIENTA was used to process some of the papers converted from PDF.
This was a great success and the annotations provided by SAPIENTA seemed to be
accurate.
